\chapter*{Acknowledgements}
\markleft{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

\paragraph{Personal acknowledgements}

First and foremost, I would like to express my gratitude to my tutor, Mr. Talbi, for his guidance and for giving me the opportunity to work on this subject, even though it was outside my primary field of study. I also extend my appreciation to the BONUS research team for their warm welcome and support throughout the internship.  

On a more personal note, I am deeply thankful to my girlfriend for her patience and willingness to listen as I tried to explain the intricacies of my work during the internship. Her encouragement meant a great deal to me during this journey.  

Lastly, I would like to acknowledge several people at the \acrfull{utt} for their essential contributions to my experience. I am especially grateful to Ms. Makboul for her support, guidance, and advice regarding my professional development. My thanks also go to Ms. Goffroy from the corporate relations department for her responsiveness and assistance during the internship process. Finally, I am indebted to all the professors who took the time to answer my questions about academic careers, particularly Mr. Afsar, Mr. Hnaien and Ms. Yalaoui, whose help was crucial in securing this internship opportunity.


\paragraph{Offical acknowledgements}
This work was partially supported by the EXAMA (Methods and Algorithms at Exascale) project under grant ANR-22-EXNU-0002.\\ 

Experiments presented in this paper were carried out using the Grid'5000 testbed, supported by a scientific interest group hosted by Inria and including CNRS, RENATER and several Universities as well as other organizations (see https://www.grid5000.fr).\\

Note on the use of AI : ChatGPT has been used to write this report of text polishing (correct remaining English mistakes, reformulates sentences, maintain consistence in the terms used across the document) and as a help to write some of \LaTeX components.